Benchmarking of quantum processors with random circuits

### 2018-06-07 paper/paper.tex
small change

To summarize, results from real devices running circuits generated with randomly chosen pairings for the inverse slices were compared to those from simulated instances of both random and correctly chosen pairings. Without error mitigation, the results from the real devices were found to correspond more closely to the simulations of the random pairings, which shows the potent effect of the noise in washing away the expected structure from the outputs. Behaviour much closer to the case of correctly chosen pairings were found when error mitigation was used, especially for the 5 and 16 qubit IBM devices and 8 qubit Rigetti device. This was especially true for the first round, which represents circuits with a CNOT depth of 2. The strong positive effects of error mitigation show that the devices do indeed have powerful capabilities, but techniques for error mitigation will be very important for unlocking them in the near-term.

>>>>

To summarize, results from real devices running circuits generated with randomly chosen pairings for the inverse slices were compared to those from simulated instances of both random and correctly chosen pairings. Without error mitigation, the results from the real devices were found to correspond more closely to the simulations of the random pairings, which shows the potent effect of the noise in washing away the expected structure from the outputs. Behaviour much closer to the case of correctly chosen pairings were found when error mitigation was used, especially for the 5 qubit IBM device and with strong effects also for the 16 qubit IBM device and 8 qubit Rigetti device. The strong positive effects of error mitigation show that the devices do indeed have powerful capabilities, but techniques for error mitigation will be very important for unlocking them in the near-term.
